### 2016-03-14 paper1.tex
Put chapter headings in included files.
Added a bit more text to transition between chapters. Now on to real editing...

>>>>

\chapter{Detection of Low-Mass-ratio Stellar Binary Systems}
\label{chap:pilot}
We now turn back to the variant of the direct spectral detection method originally discussed in Chapter \ref{chap:dsd}, in which the targets are very early-type, rapidly-rotating stars. This chapter was previously published \citep{Gullikson2013_2}. The co-author, Sarah Dodson-Robinson, was my advisor at the time and provided much of the idea for the project.

### 2016-03-14 paper2.tex
Added a bit more text to transition between chapters. Now on to real editing...

\chapter{Future Direct Spectroscopic Detection of Hot Jupiters with IGRINS}
\label{chap:hotjup}
This chapter was previously published \citep{Gullikson2013}. The co-author, Mike Endl, was my co-supervisor at the time and provided much of the inspiration for the work as well as a great deal of technical assistance.

>>>>

\chapter{Future Direct Spectroscopic Detection of Hot Jupiters with IGRINS}
\label{chap:hotjup}
Several authors have used a variant of the method we described in  Chapter \ref{chap:psi1dra} to search for emission from ``Hot Jupiter`` planets orbiting a sun-like star. In this case the flux ratio is much more extreme, but still possible with enough high signal-to-noise ratio spectra. In this chapter, we generate simulations of the IGRINS instrument to assess whether it can detect Hot Jupiter emission. This chapter was previously published \citep{Gullikson2013}. The co-author, Mike Endl, was my co-supervisor at the time and provided much of the inspiration for the work as well as a great deal of technical assistance. While the instrument was being built at the time of publication, it is now functioning on the 2.7m telescope at McDonald Observatory and a pilot survey based on this work is in progress.
